### 2022-03-18 doc/contrastive-learning.tex
updates CME results

                CME - Full, Contrast                            & 0.899          & 0.960          & 0.820          & 0              & 0.369          & 0.527          & 0.584          & 0.757          & 0.849          & 0.551          & 0.713          & 0.697          & 0.529          & 0.635          \\

@@

>>>>

                CME - Full, Contrast                            & 0.892          & 0.960          & 0.828          & 0              & 0.307          & 0.558          & 0.554          & 0.767          & 0.847          & 0.505          & 0.725          & 0.793          & 0.542          & 0.637          \\

@@

\subsubsection{18.03.2022 - Image to 3D full pretraining}

\textbf{Details:} Using the 3D features learned previously, the goal was to transfer these features to the 3D points. Here I used a 3D to 2D contrastive loss with no additional 3D-3D contrastive loss.

\textbf{Results:} It seems to improve performance slightly. The biggest difference is that it starts at a significantly lower loss (2.5 vs 2.8) and thus goes down slightly quicker than without pre-training. The visualization also shows a big difference in terms of making sense of the points.
